High-Dim Project

### 2014-12-18 highdim-paper/paper.tex

%
% File acl2014.tex
%
% Contact: koller@ling.uni-potsdam.de, yusuke@nii.ac.jp
%%
%% Based on the style files for ACL-2013, which were, in turn,
%% Based on the style files for ACL-2012, which were, in turn,
%% based on the style files for ACL-2011, which were, in turn, 
%% based on the style files for ACL-2010, which were, in turn, 
%% based on the style files for ACL-IJCNLP-2009, which were, in turn,
%% based on the style files for EACL-2009 and IJCNLP-2008...

@@

\end{document}

>>>>

<<<<<<< HEAD
%
% File acl2014.tex
%
% Contact: koller@ling.uni-potsdam.de, yusuke@nii.ac.jp
%%
%% Based on the style files for ACL-2013, which were, in turn,
%% Based on the style files for ACL-2012, which were, in turn,
%% based on the style files for ACL-2011, which were, in turn, 
%% based on the style files for ACL-2010, which were, in turn, 
%% based on the style files for ACL-IJCNLP-2009, which were, in turn,
%% based on the style files for EACL-2009 and IJCNLP-2008...

@@

\end{document}
=======
%
% File acl2014.tex
%
% Contact: koller@ling.uni-potsdam.de, yusuke@nii.ac.jp
%%
%% Based on the style files for ACL-2013, which were, in turn,
%% Based on the style files for ACL-2012, which were, in turn,
%% based on the style files for ACL-2011, which were, in turn, 
%% based on the style files for ACL-2010, which were, in turn, 
%% based on the style files for ACL-IJCNLP-2009, which were, in turn,
%% based on the style files for EACL-2009 and IJCNLP-2008...

\author{name1 \\
  Columbia University\\
  {\small \tt uni1@columbia.edu} \\\And
  name2 \\
  Columbia University\\
  {\small \tt uni2@columbia.edu} \\\And
  name3\\
  Columbia University\\
  {\small \tt uni3@columbia.edu} \\}
\date{}

\section{Introduction}

$$ \min_{W \in R^{d x m}} F(W) = $$
$$\frac{1}{n} \sum_{i=1}^{n} \sum_{r \neq y_i } \max(1 - ( W_{:y_i}^T \cdot x_i - W_{:r}^T \cdot x_i) , 0 )^2 $$
$$ + \lambda \sum_{g \in \mathcal{G}} \sum_{r=1}^{d} \| W_{g,r} \|_2$$ \\

The first term is the multiclass squared hinge loss function. We want the dot product of an instance and its feature vector to be as large as possible, and the dot product of this instance and the rest feature vectors to be as small as possible. And as long as their difference is greater then a margin ($1$ in this case), we won't penalize it. In the second term, $W_{g,r}$ means a block of weights in group $g$ and class $m$. The L2-norm regulization is computed and sum up for each block. The $\lambda > 0$ is a parameter controls the trade-off between the hinge loss and the L2-norm regulization.  \\

\subsection{Artificial Data}

\begin{figure}[ht]
\begin{center}
	\includegraphics[width=5cm, natwidth=200, natheight=206]{m_img}
	\caption{Group-wise sparse weight matrix generated: 5 classes, 25 features in 5 groups}
\end{center}
\end{figure}

Then we generate random vectors, each of which has a length of the number of all features, and calculate dot product with the weight matrix W to get the class assignments for these random vectors. The random vetors X and the class assignments Y make up the training data set. \\

\subsection{Artificial Data}

Shape Recovery. One of the main indicator of the effectiveness of our model is to see whether the calculated weight matrix is sparse group-wise. Our experiments show so. The following figures shows in a typical trial, the generated target weight matrix and the recovered weight matrix by our model. By comparing them side by side, we can tell that their sparsity patterns are similar.

\begin{figure}[ht]
\begin{center}
	\includegraphics[width=5cm, natwidth=200, natheight=307]{m1_img}
	\caption{Target group-wise sparse weight matrix generated: 5 classes, 25 features in 5 groups}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
	\includegraphics[width=8cm,natwidth=200, natheight=186]{m2_img}
	\caption{Weight matrix calculated from the training data. It's similar to the one generated.}
\end{center}
\end{figure}

The different weights between the calculated matrix and the target matrix can be due to many factors. First, sample coverage is a major factor. In our simulation data, the sample size is small. Limited by the time complexity of the algorithm, it's difficult to complete the computation for a very large sample size in a reasonable time. Also, the sampling is random. There is no guaranteed that the inferred weights leads to the target weights. \\

Accuracy. In our experiments, the generator algorithm was configured to produce 150 random vectors from the underlying model where it consists of 5 classes and 25 features in 5 groups. The accuracy achieved was about $60\%$ to $70\%$. \\

\end{document}
>>>>>>> FETCH_HEAD
